\documentclass[english,a4paper,nologo,nototpages]{europasscv}


% add Personal information
\ecvname{Fabio Di Carlo}
\ecvaddress{00136, Roma, Italy}
%\ecvtelephone{(+39) 555 55 55 555}
\ecvmobile{(+39) 329 0707 958}
%\ecvworkphone{(+39) 555 55 55 555}
\ecvemail{dicarlo.fa@gmail.com}
%\ecvhomepage{dicaeffe.wordpress.com}%www.dicaeffe.me}
%\ecvgitpage{https://www.git.example.org/}
%\ecvgithubpage{github.com/dicaeffe}
%\ecvgitlabpage{gitlab.com/dicaeffe}
%\ecvlinkedinpage{www.linkedin.com/in/fabio-di-carlo/}
%\ecvorcid[label, link]{0000-0000-0000-0000}
%\ecvim{AOL Messenger}{dicaeffe}
%\ecvim{Skype}{dicarlo.f}
%\ecvim{Google Talk}{dicaeffe}
\ecvdateofbirth{25th of July, 1987}
\ecvnationality{Italian}
%\ecvgender{Male}


% add a photo
%\ecvpictureleft[options]{filename}
%\ecvpictureright[options]{filename}
%\ecvpicture[width=3.8cm]{picture.jpg}

% begin document environment
\begin{document}
    
    % begin europass environment
    \begin{europasscv}
        % add all personal information
        \ecvpersonalinfo
        
        % job application description
        %\ecvbigitem{Job applied for}{Insert the job application title}
        
        \ecvhighlight{About me}: I am master of science graduate looking to take the next step to strengthen my skills on team management and solution design. My strengths are the good critical thinking and problem solving skills. I enjoy working in a team and I love to keep an open-minded, interdisciplinary curiosity to anything that surround me: this encourages me to think out of the box and to find new motivation.
        
        % begin Work Experience section
        \ecvsection{Work Experience}
        
        \ecvtitle{Dec 2021 -- Present}{Notartel}
        \ecvitem{}{Rome, Italy}
        
        \ecvitem{dec 2021 -- Present}{\ecvhighlight{Solution and Architecture Designer}}
        \ecvitem{}{Project management, design and development of back-end solutions in line with the guidelines and regulations for the italian notary sector.\newline
        \textbf{Tech}: Java, Spring Boot, JUnit, GIT, MySQL, Python, S3.\newline
        \textbf{Other}: Agile, RESTful APIs, PM (Gantt, Wbs), Sequence Diagram, MS Office, Redmine, Nextcloud.}
        
        \ecvtitle{Sep 2015 -- Nov 2021}{Accenture}
        \ecvitem{}{Rome, Italy}
        
        \ecvitem{dec 2019 -- nov 2021}{\ecvhighlight{Senior Analyst}}
        \ecvitem{}{Analysis of complex problems, design and development of solutions impacting a company's PaaS, management of scrum backlog, management of code lifecycle, creation and training of a neural network for a carpooling project.\newline
        \textbf{Tech}: Java, Spring Boot, JUnit, GIT, MySQL, Python.\newline
        \textbf{Other}: Agile (Scrum), IoT, RESTful APIs, Sequence Diagram, MS Office, Jira, SharePoint.}
        
        \ecvitem{jun 2018 -- nov 2019}{\ecvhighlight{Analyst}}
        \ecvitem{}{Development of microservices with RESTful APIs for an IoT platform, analysis of requirements, code quality (Sonar).}
        
        \ecvitem{sep 2015 -- may 2018}{\ecvhighlight{Associate Analyst}}
        \ecvitem{}{Development of a CRM (telco), end-to-end tests of tablet and mobile app (banking), customization of the WSO2 API-Manager for an IoT platform, refactoring of a microservice in order to create RESTful compliant APIs.}
        
        % begin Education and Training section
        \ecvsection{Main Education and Training}
        
        \ecvtitle{Jun 2021}{Microsoft Certified: Azure Fundamentals AZ-900}
        
        \ecvtitle{Aug 2017}{Accenture Technology Academy 2.0 with MIT}
        \ecvitem{}{Company's certification developd with MIT about Artificial Intelligence, Delivery methods, Internet of Things}
        
        \ecvtitlelevel{May 2015}{Master of Science, Physics}{ISCED~7}
        \ecvitem{}{Sapienza, Università di Roma, Rome, Italy\newline
        \ecvhighlight{Thesis}: "\textit{Agent Based Modeling of the Emergence of Social Norms}"\newline
        Data modeling, problem solving, be able to connect theory and experience and the study of modern physics such as:
            - Complex Systems
            - Statistical Mechanics
            - Condensed and Soft Matter
            - Biophysics
            - Mathematical Modelling
            - Quantum Relativistic Mechanics
            - Scientific coding (C Language) and \LaTeX
        }
        
        % begin Other Training section
        \ecvsection{Other Edu-Training}

        \ecvtitlelevel{Nov 2011}{Bachelor of Science, Physics}{ISCED~6}
        \ecvitem{}{Sapienza, Università di Roma, Rome, Italy\newline
        \ecvhighlight{Thesis}: "\textit{Detectors for Positron Emission Tomography}"\newline
        Studies of Classical and Modern Physics
%        - Quantum Physics
%        - Rational Mechanics
%        - Mathematical Analysis and Analitical Geometry
%        - Spectrometry and Astrophysics
%        - Particle Physics
        }
        
        \ecvtitle{Jun 2019}{BLS-D - Basic Life Support and Defibrillation}
        
        \ecvtitle{May 2017}{HACCP}
        
        \ecvtitle{Jun 2012}{Wood Badge - Unit Leader Training}
        \ecvitem{}{International certification for Scout Unit Leaders released by WOSM (World Organization of the Scout Movement)}
        
        \ecvtitle{Apr 2012}{Corporate Social Reporting}
        \ecvitem{}{Course financed by italian Ministry of Labour.}
        
        \ecvtitle{Apr 2011}{Medal of Pubblica Benemerenza 3° Class 1° Fascia}
        \ecvitem{}{Decree april the 12th 2011, G.U.n.125 may the 31st 2011}
        
        \ecvtitlelevel{Jun 2006}{Diploma Liceo Scientifico - Piano Nazionale Informatico}{ISCED~3}
        \ecvitem{}{Liceo Scientifico Talete, Rome, Italy}
        
        \ecvtitle{Dec 2004}{ECDL - European Computer Driving Licence}
        \ecvitem{}{AICA - Associazione Italiana per l'Informatica ed il Calcolo Automatico, Italy}
        
        % begin Other Training section
        \ecvsection{Volunteering}
        
        \ecvtitle{Sep 2006 -- Sep 2021}{Unit Leader - Educator}
        \ecvitem{}{CNGEI - Associazione Scout Laica\newline
        I was responsible of the organization of all activities and events of the group, aiming to educate the youth through the Scout values. In addition I managed my staff and all group's resources.}
        
        \ecvtitle{May 2008 -- Sep 2011}{Protezione Civile}
        \ecvitem{}{
            \begin{ecvitemize}
                \item Emergency earthquake Abruzzo 2009: relations with citizens, office and logistic services.
                \item Summer Educative Camps AIB (CNGEI and DPC partnership) 2008-2010-2011.
            \end{ecvitemize}
        }
        
        % begin Personal skills section
        \ecvsection{Personal skills}
        
        %begin Language Skills section
        \ecvmothertongue{Italian}
        \ecvlanguageheader
        %\ecvlanguage{English}{B1}{B2}{B1}{B2}{B2}
        %\ecvlanguagecertificate{First Certificate in English (FIRST) B2}
        \ecvlastlanguage{English}{B1}{B2}{B1}{B2}{B2}
%        \ecvlanguagefooter

%        \ecvdigitalcompetence
%            {\ecvBasic}
%            {\ecvIndependent}
%            {\ecvProficient}
%            {\ecvIndependent}
%            {\ecvBasic}
        
        \ecvblueitem{Artistic skills}{Good hand drawing skills and basic knowledge of vectoral graphics (with Corel Draw) and UNITY engine}
        
%        \ecvblueitem{Communication skills}{}
        
        \ecvblueitem{Driving Licence}{B - Released by Motorizzazione Civile, Rome, Italy}
        
        \ecvblueitem{Privacy}{In compliance with the GDPR, I authorize the process of personal data in this document}
    \end{europasscv}
    
\end{document}



% References:
% europasscv guide: https://ctan.mirror.garr.it/mirrors/ctan/macros/latex/contrib/europasscv/europasscv.pdf
